---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->


# OntarioGeoHubR
An R package that will make it easy to fetch resources from Ontario
geohub and pull them into R for subsequent analysis and reporting.
Currently supported endpoints include:

+ Fisheries Management Zones
+ MNR Districts
+ Conservation Authorities
+ Waterbodies
+ Provincial Parks
+ Townships

More endpoints and improved filters can be added in the future.

The functions in the package do not perform any calculations, they
simply fetch the data from the specified endpoint and can be thought
of as a short cut for manually access geohub, downloading the
resources and reading the files in.



```{r setup}
# ggplot2 isn't required, but used here for plotting.

library(ggplot2)
library(OntarioGeohubR)
```



# Fisheries Management Zones

Fisheries Management Zones are the main spatial unit used by the
Ontario Ministry of Natural Resource to manage fisheries resources
across the province.

the function `fetch_fmz()` can be used to retrieved one or more
fisheries management units and return them as a sf (simple feature)
which can then be used for plotting or subsequent analysis.

```{r fmz}
fmz <- fetch_fmz(10)
unique(fmz$FISHERIES_MANAGEMENT_ZONE_ID)

fmz <- fetch_fmz(c(10, 11, 12))
unique(fmz$FISHERIES_MANAGEMENT_ZONE_ID)

my_plot <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = fmz, aes(fill = FISHERIES_MANAGEMENT_ZONE_ID))
print(my_plot)
```


# MNR Districts

MNR Districts divide the Regions of the province into smaller
organizational units for the purpose of managing Ministry programs and
resources at a district level.

The function `fetch_mnr_district()` can be used to retrieved one or
more districts that match a string (or vector of strings).


```{r district}
dist <- fetch_mnr_district(name_like = "Aurora")
unique(dist$DISTRICT_NAME)

dist <- fetch_mnr_district(name_like = c("Aurora", "Owen Sound"))
unique(dist$DISTRICT_NAME)

my_plot <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = dist, aes(fill = DISTRICT_NAME))
print(my_plot)
```

# Conservation Authorities

The function `fetch_conservation_authority()` accesses the geohub
endpoint for conservation authority administrative areas and returns
geometries that represent lands under the jurisdiction of a
Conservation Authority.  The function `fetch_conservation_authority()`
can be given a string or a vector of strings and will return
conservation area object(s) with names that match.

```{r conservation_authority}
ca <- fetch_conservation_authority(name_like = "Saugeen")
unique(ca$COMMON_NAME)

ca <- fetch_conservation_authority(name_like = c("Saugeen", "Maitland"))
unique(ca$COMMON_NAME)

my_plot <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = ca, aes(fill = COMMON_NAME))
print(my_plot)
```

# Waterbodies

The function `fetch_waterbody()` accesses the geohub endpoint 'Ontario
waterbody location identifier' which represents unique Ontario
waterbody location identification information.  The function
`fetch_waterbody()` can be used to retrieve waterbodies by Waterbody
Identifier or partial matches to various name fields.



```{r waterbody}
wby <- fetch_waterbody(name_like = "Lake of the")
print(
  wby[
    ,
    c(
      "WATERBODY_IDENT",
      "OFFICIAL_NAME",
      "WATERBODY_IDENT",
      "UNOFFICIAL_NAME",
      "OFFICIAL_ALTERNATE_NAME",
      "EQUIVALENT_FRENCH_NAME"
    )
  ]
)

wby <- fetch_waterbody(name_like = c("Saugeen", "Bruce"))

print(
  wby[
    ,
    c(
      "WATERBODY_IDENT",
      "OFFICIAL_NAME",
      "WATERBODY_IDENT",
      "UNOFFICIAL_NAME",
      "OFFICIAL_ALTERNATE_NAME",
      "EQUIVALENT_FRENCH_NAME"
    )
  ]
)


my_plot <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = wby, aes(fill = WATERBODY_IDENT))
print(my_plot)


wby <- fetch_waterbody(wbylid = "15-3726-54565")
print(
  wby[
    ,
    c(
      "WATERBODY_IDENT",
      "OFFICIAL_NAME",
      "WATERBODY_IDENT",
      "UNOFFICIAL_NAME",
      "OFFICIAL_ALTERNATE_NAME",
      "EQUIVALENT_FRENCH_NAME"
    )
  ]
)

# Lake of the Woods and Slippery Lake (to the north west of LOW)
wby <- fetch_waterbody(wbylid = c("15-3726-54565", "15-3726-54565"))
print(
  wby[
    ,
    c(
      "WATERBODY_IDENT",
      "OFFICIAL_NAME",
      "WATERBODY_IDENT",
      "UNOFFICIAL_NAME",
      "OFFICIAL_ALTERNATE_NAME",
      "EQUIVALENT_FRENCH_NAME"
    )
  ]
)

my_plot <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = wby, aes(fill = WATERBODY_IDENT))
print(my_plot)
```

# Provincial Parks

Areas regulated under the provincial Parks Act (2006) can be retrieved
using the function `fetch_provincial_parks()`.  This function can be
given a string or a vector of strings and will return parks with names
that match those strings


```{r parks}
ppark <- fetch_provincial_park(name_like = "Algonquin")
unique(ppark$COMMON_SHORT_NAME)

ppark <- fetch_provincial_park(name_like = c("Algonquin", "Inverhuron"))
unique(ppark$COMMON_SHORT_NAME)

my_plot <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = ppark, aes(fill = COMMON_SHORT_NAME))
print(my_plot)
```


# Townships

Townships are the fundamental land subdivision for the province of
Ontario.  The function `fetch_township()` can be given a string or a
vector of strings and will return township object with names that match.

```{r townships}
twnshp <- fetch_township(name_like = "Saugeen")
unique(twnshp$OFFICIAL_NAME)

twnshp <- fetch_township(name_like = c("Saugeen", "Bruce"))
unique(twnshp$OFFICIAL_NAME)

my_plot <- ggplot2::ggplot() +
  ggplot2::geom_sf(data = twnshp, aes(fill = OFFICIAL_NAME))
print(my_plot)
```
